---
title: "Some High-level RAVE Functions"
author: "Zhengjia Wang"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

RAVE is GUI-driven, but it is not an omni tool that provides everything. At some point, you will need to program by yourself. RAVE provides both high-level and low-level functions for you to load data. This tutorial mainly introduce high-level classes and functions.

* High-level functions require the subjects to be preprocessed using RAVE infrastructure. 

### Subject utility

You can get a subject class by

```{r}
subject = raveio::as_rave_subject("demo/DemoSubject")
print(subject)
```

The RAVE subject class provides access to all the meta information. For example,

```{r}
# electrodes.csv
electrode_table = subject$get_electrode_table()
## Un-comment to print
# print(electrode_table)

# Trial epochs
subject$epoch_names
epoch = subject$get_epoch("auditory_onset")
## Un-comment to print
# print(epoch$table)

# References
subject$reference_names
reference_table = subject$get_reference("default")
## Un-comment to print
# print(reference_table)
```

> Hint: Type `subject$` and wait or press `Tab` key in RStudio to get autocompletion for all possible fields and methods.

### Electrode channels

Once electrode channel data is imported, you can create electrode instances:

```{r}
# channel 14
e14 = raveio::new_electrode(subject, 14)
```

To load data from this channel, you will need to set which epoch and trial intervals. If the channel is referenced, you might also want to set reference channel as well. 

```{r}
# set loading epoch
epoch = subject$get_epoch("auditory_onset")
e14$set_epoch(epoch)

# set loading time window from 1s before onset and 2s after onset
e14$trial_intervals = c(-1, 2)

# set reference channel, using channel 13 as reference
ref = raveio::new_reference(subject, 13)
e14$set_reference(ref)
```

Now you can load voltage

```{r}
voltage_data = e14$load_data("voltage")
str(dimnames(voltage_data))
```

In many scenarios, the loaded data could be too large for the computer memories. RAVE stores the loaded data as `FileArray` - a format that stores data on disk and loads data only when needed. To get the numerical values, simply use `[]` operator:

```{r}
vdata = voltage_data[drop = FALSE]
# Snapshot the data
str(vdata)
```

Let's plot the `vdata`

```{r}
# Convert to trial x time
vdata_transform = t(vdata[,,1])
ravetools::plot_signals(
  vdata_transform,
  sample_rate = 2000,
  time_shift = -1,
  ylab = "Trial",
  main = "Channel 14 (ref=13) voltage over time by trials"
)
```

### Pre-designed data repository

If you have finished RAVE preprocessing (Notch filter, wavelet, epoch, re-referencing), instead of loading channels one-by-one, you can use built-in data loading functions. These functions start with `raveio::prepare_*`. For example, if you want to 

1. load the power spectrogram for channel 14 and 15
2. Baseline the data (baseline window: `-1~-0.5`)
3. Subset trial data on stimulus `drive_av`
4. Plot the average power percentage change

```{r, fig.width=12, fig.height=6}
# ---- Load data --------------------------------
repository = raveio::prepare_subject_power(
  subject,
  electrodes = c(14, 15),
  reference_name = "default",
  epoch_name = "auditory_onset",
  time_windows = c(-1, 2), 
  verbose = FALSE
)

# ---- Baseline --------------------------------
repository <- raveio::power_baseline(repository,
                                     baseline_windows = c(-1, -0.5),
                                     method = "percentage")

# ---- Get baseline'd power, and subset --------
trial_nums =
  repository$epoch$trials[ repository$epoch$table$Condition %in% c("drive_av") ]

sliced_data = subset(
  repository$power$baselined,
  Trial ~ Trial %in% trial_nums
)
str(sliced_data)

# ---- Collapse by trial and electrodes and plot 
# keep = c(2, 1, 4) means keep the 1st (Frequency), 2nd (Time) ,
#   and 4th (Electrode channel) dimensions
#   and transpose the first two, so the result is 
#     Time x Frequency x Electrode
avg_data = raveio::collapse2(x = sliced_data,
                              keep = c(2, 1, 4),
                              method = "mean")

# plot: set up layout
ravebuiltins:::layout_heat_maps(k = 2, max_col = 2)
par(cex.lab = 2, cex.main = 3, cex.axis = 2,
    mar = c(4.1, 6.1, 4.1, 1.1))

# color palette
pal = ravebuiltins::expand_heatmap("BlueWhiteRed")

# plotting range
zlim = max(avg_data) * c(-1, 1)

# draw channel 14
image(x = repository$time_points,
      y = repository$frequency,
      z = avg_data[,,1], col = pal, zlim = zlim,
      xlab = "Time (s)", ylab = "Frequency (Hz)",
      main = "Ch14 - drive_av")

# draw channel 15
image(x = repository$time_points,
      y = repository$frequency,
      z = avg_data[,,2], col = pal, zlim = zlim,
      xlab = "Time (s)", ylab = "Frequency (Hz)",
      main = "Ch15 - drive_av")

# draw legend
legend_ticks = seq(zlim[[1]], zlim[[2]], length.out = length(pal))
image(y = legend_ticks, z = matrix(legend_ticks, nrow = 1),
      col = pal, axes = FALSE, xlab = "", ylab = "Baseline % Change of Power")
axis(side = 2, at = c(zlim, 0), labels = c(sprintf("%.2f", zlim), "0"))
```



### 3D viewer

Here is a simple example for plotting the brain (more tutorials on 3D viewers will come soon)

```{r, eval=FALSE}
brain = raveio::rave_brain(subject)
plot(brain)
```

